Language learning in context via recursive pragmatic reasoning

### 2013-05-31 praglearn.tex
clarify wording in scalar implicature section

The recursive pragmatic reasoning portions of our model capture
findings on specificity implicature. Consider a representation of
scalar implicature as a matrix $\left[
    \begin{array}{cc}
      0.5 & 0.5 \\
      0 & 1
    \end{array}
  \right]$, where rows show the words ``some'' and ``all'' and columns
  indicate worlds where {\sc some but not all} and {\sc all} are true,
  respectively, capturing the regularity that ``some'' can be said of
  situations where {\sc all} is actually the case. Assuming uniform
  costs for the two words, a rational speaker confronted with such a
  lexicon will prefer to say ``some'' only when they mean \textsc{some
    but not all}, and this is therefore the interpretation that a
  rational listener will place on ``some'' as well.

>>>>

The recursive pragmatic reasoning portions of our model capture
findings on specificity implicature. Consider a lexicon in which the
rows represent the meaning of ``some'' and ``all'', and the columns
indicate worlds where \textsc{some-but-not-all} and \textsc{all} are
true, respectively: $\left[
    \begin{array}{cc}
      0.5 & 0.5 \\
      0 & 1
    \end{array}
  \right]$. This lexicon captures the regularity that ``some'' can be said of
  situations where {\sc all} is actually the case. Assuming uniform
  costs for the two words, a rational speaker confronted with such a
  lexicon will prefer to say ``some'' only when they mean \textsc{some
    but not all}, and this is therefore the interpretation that a
  rational listener -- and our model -- will place on ``some'' as well.
